DTOADQ

### 2017-11-27 testdocs/_region_.tex
doicumentation
whatever

\message{ !name(paper.tex)}\documentclass{article}
\usepackage{amsmath}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{color}
\usepackage{graphicx}
\graphicspath{ {../screenshots/} }
\usepackage[margin=1.15in]{geometry}

@@

\message{ !name(paper.tex) !offset(-3) }

@@

  \section{SDFs}
  In order to compute a normal of an SDF, you must perform a gradient approximation: the central distance onf the SDF at
  P. For example, the difference quotient:
  \[\frac{(f(x+h) - f(x))}{h}\]
  \begin{align*}
    S(P, R) &= P - R^2   & \text{SDF of a sphere Radius  }\\
    S(P, N) &= P \cdot N  & \text{SDF of a plane at Normal}\\
    S(P, H, R) &= <|P_{x, z}| - R, \: P_{y}> - H & \text{SDF of a torus with
                                                  Radius and Hole}\\
  \end{align*}
  \section{OpenCL}
  \section{Light Transport Introduction}
  \section{Bidirectional Path Tracing}
    The main foundation of the mathematics and theory have come from many sources, from Veach's PhD thesis to PBR 3rd ed. and various open source path tracing kernels such as NanoRT, Embree, etc. However, the implementation differs from these in that the algorithm is optimized for the GPU. This section is about transforming the algorithms and mathematical models from Veach's thesis into something easily and efficiently implementable the GPU.

    Calculating probability distribution functions is a very vital component in
    Monte Carlo Sampling. The PDF states the probability of a random variable to
    take the form of a given input. Its usefulness comes when contributions from
    many Monte Carlo samples have a different weight. That is, one sample may
    have a higher probability distribution, and thus a higher contribution to
    the path. That's the strategy behind Monte Carlo;
    \begin{align}
      \int f(x) \approx \frac{1}{N}\Sigma_0^N\frac{f(x)}{p(x)}
    \end{align}
    The PDF applies to everything from path contributions, solid angles of a
    BRDF, uniformly sampling a sphere, etc. I had a difficult time understanding
    these, and more importantly, how to calculate them for a given formula. The
    biggest conceptual barrier is that, for example, given a solid angle in a
    hemisphere $\Omega$, the probability for a random variable X to equal
    $\omega$ is 0. But this isn't what's happening here, this is all about the
    probability that X could potentially equal $\omega$ when compared to other values
    in $\Omega$. It's all about comparing the probabilities of two potential
    $\omega$s with each other.

    I still have a hard time conceptualizing these things in my head, but the
    good thing is, is that calculating these are relatively easy. There's a lot
    that could be talked about, but the important thing is that I've found a
    reliable three-step process. The first is to
    find the cumulative distribution function $CDF = Pr(X \leq x)$. Where $Pr$
    is the probability, $X$ is a uniformly random variable, and $x$ is a known
    constant. In other words, this gives the probability that, for a formula
    $P$, where $X \in \Omega$, and $\Omega$ is the set of all possible values
    for $CDF$,
    that $X \leq x$. The second step is to take the derivative of this, so for
    PDF $p$
    \begin{align}
      p(x) = \frac{dCDF(x)}{dx}
    \end{align}
    And the final step is to verify that the PDF is correct by integrating it
    over $\Omega$, this final value should equal 1. This makes sense intuitively
    -- it is a probability after all, so the sum of the probabilities of every
    possible input must be 1.
    For an example, how I calculated the PDF of an area light source
      $L^0_e(v) = L_o(P, \omega_o)$ 
    is quite simple. Firstly,the area light is defined as a sphere, and thus our
    set of all possible values is correlated to surface area:
    $\Omega = [0,\:2.0f*\tau*R^2]$.
    Thus for a given constant $x$, and a uniformly random $X$,
    \begin{align}
      CDF(x) = Pr(X \leq x) = \frac{x}{2.0f*\tau*R^2}\\
      p(x) = \frac{dCDF(x)}{dx} = \frac{1.0f}{2.0f*\tau*R^2}\\
      \int_0^{\Omega}p(x)dx = 1.0f
    \end{align}
    In code
    \begin{lstlisting}
      float Light_PDF ( float3 P, Emitter* m ) {
        float rad_sqr = m->radius*m->radius;
        return 1.0f/(2.0f*TAU*rad_sqr);
      }
    \end{lstlisting}
    The more interesting aspect, in this example, is actually generating the
    uniformly distributed samples of a sphere. The naive method gives incorrect
    distributions.TODO {page 774}

    The most obvious way to calculate this is the six-point gradient; where for
    each axis you compute $f(x+h) - f(x-h)$, and normalize the result. This
    returns a vector pointing in the direction where the map's SDF changes the
    most: the normal. A four point gradient is possible; as long as each each
    point of the gradient is multiplied by $\epsilon$ before normalizing. The
    speedup from six to four is worthwhile, as computing each gradient is
    expensive as it involves a sdf map call. There are more utilities with
    gradients not yet currently provided in DTOADQ but are worth mentioning, a
    few are: an additional normal call using an alternative (higher-quality) SDF
    map can be used to compute a 'normal' bumpmap, and analyzing the gradient by
    hand allows a cheap normal computation of primitives such as a spheres.

    Rendering equation with solid angle:
  \begin{align}
    L_o(P, \omega_o) = L_o(P, \omega_o) + \int_{\Omega}f_s(P, \omega_i,
    \omega_o) L_i(P, \omega_i) cos\Theta_i d\omega_i
  \end{align}
    To get from solid angle to path, consider:
  \begin{align}
    f_s(v \rightarrow \dot{v} \rightarrow \ddot{v}) &= f_s(P, \omega_i,
                                                      \omega_o)\\
    L_e(v \rightarrow \dot{v}) &= L_e(P, \omega_o)\\
    L_e(v \rightarrow \dot{v}) &= L_e^0(v) L_e^1(v \rightarrow \dot{v})
  \end{align}
    That is, instead of looking at a point $P$ with an incoming and outgoing
    angle $(\omega_i,\:\omega_o)$, look at the path from $P_{-1}$ ($v$) to
    $P_{+1}$ ($\ddot{v}$). More accurately, it's the transport between
    three different surfaces of the scene. In terms of SDFs, the surface
    is every point on an SDF map where $|map| \leq \epsilon$. There's no longer
    any integration over a hemisphere with solid angle $\omega_i$, it's now over
    every single surface in the scene. This will be explained in detail later.
\\
    In the case of $L_e$,
    DTOADQ [at least, for now], only has support for area-light. Thus consider:

@@

  \section{Bibliography}
  [1]
  \begin{align*}
    \Sigma_{k=1}^{\infty} \int_{M^{k+1}} L_e(v_0 \rightarrow v_1) G(v_0
    \leftrightarrow v_1)
    \Pi_{i=1}^{k-1} F_s(v_{i-1} \rightarrow v_i \rightarrow v_{i+1}) G(v_i
    \leftrightarrow v_{i+1})\\
    W_e^j(v_{k-1} \rightarrow v_k) dA(v_0) \ldots dA(v_k)
  \end{align*}
\end{document}

\message{ !name(paper.tex) !offset(-459) }

>>>>

\message{ !name(test.tex)}\documentclass{article}
\usepackage{amsmath}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{color}
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage[margin=1.15in]{geometry}

@@

\message{ !name(test.tex) !offset(-3) }

@@

  \section{Signed Distance Fields}
  Signed Distance Fields (SDFs) are a mathematical tool to represent a 3D primitive by describing its surface via a distance field. Given an arbitrary point in space, the SDF of a primitive is the distance to its nearest point/surface. For example, the SDF of a sphere is $\Vert\:O\:\Vert - R$. With SDFs, it's possible to march a ray along the scene until it hits the surface of an SDF within a given bound, using the returned SDF distance as the distance to march. Some example SDFs are shown below:    \begin{align*}
  S(P, R) &= \Vert\:P\:\Vert - R & \text{Sphere with Radius}\\
  S(P, N) &= P \cdot N  & \text{Plane with Normal}\\
  S(P, H, R) &= <\Vert\:P_{x, z}\:\Vert - R, \: P_{y}> - H & \text{Torus with Radius and Hole}\\
  \end{align*}

  The biggest issue with SDFs is Lipschitz continuity. The SDFs themselves have a distance gradient, that is, their bound. The bounds of a SDF is expected to be at most 1 in order to remain Lipschitz continuous, as otherwise the SDF will appear deformed as shown below.

  \includegraphics[]{lipschittzbound}

  This is a larger problem in Light Transport than it is in raytracing because small discontinuities can impact the lighting of an entire scene. And to add to that, most interesting operations (such as the meta balls shown in the image above) will violate Lipschitz. The easiest way to fix this is to multiply the distance field by a constant to stay below 1, but this is less of a fix and more of a hack.

  In order to compute a normal of an SDF, you must perform a gradient approximation: the central distance onf the SDF at
  P. For example, the difference quotient:
  \[\frac{(f(x+h) - f(x))}{h}\]
  The most obvious way to calculate this is the six-point gradient; where for
each axis you compute $f(x+h) - f(x-h)$, and normalize the result. This
returns a vector pointing in the direction where the map's SDF changes the
most: the normal. A four point gradient is possible; as long as each each
point of the gradient is multiplied by $\epsilon$ before normalizing. The
speedup from six to four is worthwhile, as computing each gradient is
expensive as it involves a sdf map call. There are more utilities with
gradients not yet currently provided in DTOADQ but are worth mentioning, a
few are: an additional normal call using an alternative (higher-quality) SDF
map can be used to compute a 'normal' bumpmap, and analyzing the gradient by
hand allows a cheap normal computation of primitives such as a spheres.
  \section{OpenCL}
	OpenCL, and GPU programming in general, is where I am least knowledgeable or interested. Well, OpenCL is easy to work with, and I wrote my own OpenCL module to handle OCL in a rather convenient method, for example, the DTOADQ kernel call looks as such:
	\begin{lstlisting}
	shared_info.image.Lock(); // Acquire OCL Mem from OGL image object
	ocl.Run(
	  ocl.CLStoreMem(shared_info.rw_image),
	  shared_info.image.RWrite(),
	  ocl.CLStoreMem(shared_info.image_metadata),
	  shared_info.camera,
	  shared_info.timer,
	  ocl.CLPredefinedMem(imgs),
	  ocl.CLStoreMem(shared_info.ocl_material),
	  debug_values,
	  ocl.CLStoreMem(shared_info.rng_states),
	  // kernel size
	  shared_info.image.x, shared_info.image.y
	);
	shared_info.image.Unlock();

	\end{lstlisting}

	however the problem comes with dealing with the intrinsics of GPU; optimizing code for the GPU and knowing how memory and threads/workers are handled.

  	One benefit of OpenCL is its ease to debug in comparison to OpenGL. One immediate benefit is printf, which surprisingly even works on the GPU. To make printf easily readable, I only use print on the center pixel of the image. Even so, due to the complexity of light transport, the vast majority of time spent on this project went directly towards debugging the DTOADQ kernel.

  	OpenCL also makes it relatively easy to send and receive data between the host and GPU. In comparison to OpenGL, this is a big win, however, with OpenGL4.3's Shader Storage Buffer Object, this is now no longer a selling point.

  	OpenCL also has huge drawbacks. The biggest problem is getting the results to be rendered in OpenGL. TODO. Also, there are minor annoyances, like the lack of a matrix data type, no function overloads, long compile times, or variadic functions. There are also annoyances with GPU programming in general. No dedicated random function. Though, possibly, long compile times is my fault for using a mega-kernel instead of splitting it into many small kernels.

  	It seems that the GPU is not for me or DTOADQ and something I do not enjoy to use nor am good at. However, for this project, I had to deal with it. To overcome the lack of a random function, of which high quality uniform random generation is necessary for Monte Carlo simulations, I used the MWC64X algorithm. While there are better algorithms, they fail on branches which makes it useless for DTOADQ. It seemed to work well enough. The downside is that each worker/pixel needs its own random state, preserved across multiple kernel calls. There are indefinitely better solutions.
  \section{Light Transport Introduction}
  \section{Bidirectional Path Tracing}
    The main foundation of the mathematics and theory have come from many sources, from Veach's PhD thesis to PBR 3rd ed. and various open source path tracing kernels such as NanoRT, Embree, etc. However, the implementation differs from these in that the algorithm is optimized for the GPU. This section is about transforming the algorithms and mathematical models from Veach's thesis into something easily and efficiently implementable the GPU.

    Calculating probability distribution functions is a very vital component in
    Monte Carlo Sampling. The PDF states the probability of a random variable to
    take the form of a given input. Its usefulness comes when a Monte Carlo sample has a smaller or higher total contribution compared to other samples. That is, one sample may
    have a higher probability distribution, and thus a higher contribution to
    the path. That's the strategy behind Monte Carlo;
    \begin{align}
      \int f(x) \approx \frac{1}{N}\Sigma_0^N\frac{f(x)}{p(x)}
    \end{align}
    The PDF applies to everything from path contributions, solid angles of a
    BRDF, uniformly sampling a sphere, etc.

    The
    biggest conceptual barrier is that, for example, given a solid angle in a hemisphere $\Omega$, the probability for a random uniform $X$ to equal $\omega$ is 0. That's not what the PDF calculates, instead, it's the
    probability that a random uniform $X$ could potentially equal $\omega$ when compared to other $\omega\:$s.

    The good thing is that calculating these are relatively easy. The first step is to
    find the cumulative distribution function $CDF = Pr(X \leq x)$. Where $Pr$
    is the probability, $X$ is a uniformly random variable, and $x$ is a known
    constant. This gives the probability that, for a formula
    $P$, where $X \in \Omega$, and $\Omega$ is the set of all possible values
    for $CDF$,
    that $X \leq x$. Then the PDF $p$ is defined by the derivative of CDF. To verify that the PDF is correct, integrate it
    over $\Omega$, this final value should equal 1. This makes sense intuitively
    -- it is a probability after all, so the sum of the probabilities of every
    possible input must be 1.
    For an example, how I calculated the PDF of an area light source
      $L^0_e(v) = L_o(P,\:\omega_o)$ 
    is quite simple. Firstly,the area light is defined as a sphere, and thus our
    set of all possible values is correlated to surface area:
    $\Omega = [0,\:2.0f*\tau*R^2]$. Thus,
    \begin{align}
      CDF(x) = Pr(X \leq x) = \frac{x}{2.0*\tau*R^2}\\
      p(x) = \frac{dCDF(x)}{dx} = \frac{1.0}{2.0*\tau*R^2}\\
      \int_0^{\Omega}p(x)dx = 1.0
    \end{align}
    In code
    \begin{lstlisting}
      float Light_PDF ( Emitter* m ) {
        return 1.0f/(2.0f*TAU*SQR(m->radius));
      }
    \end{lstlisting}

  The rendering equation is:
  \begin{align}
    L_o(P, \omega_o) = L_e(P, \omega_o) + \int_{S}f_s(P, \omega_i,
    \omega_o) L_i(P, \omega_i) \vert cos\theta_i\vert d\omega_i
  \end{align}

  Where:
  	 $Lo(P,\:\omega_o)$ is the radiance at point $P$ in space towards direction $\omega_o$.

  	 $L_e(P,\:\omega_o)$ is the emittance at point $P$ towards $\omega_o$ (such as a lamp).

  	 $S$ is the unit sphere in which the angle $\omega_i$ is integrated over in respects to the normal at $P$. Also, this means, implicitly, that the equation is in respects to solid angle; the angle at which a primitive $A$ subtends $B$.

  	 $f_s$ is the Bidirectional Scattering Distribution Function. This will be detailed in the BSDF chapter, suffice it to say, it describes how photons are scattered (or absorbed) from point P in space from direction $\omega_i$ towards $\omega_o$ -- either through reflection (BRDF), or transmittance (BTDF). In volumetric path tracing, there is also subsurface scattering.

  	 $L_i(P, \omega_i)$ is the rendering equation at P from $\omega_i$

  	 And $cos\theta_i$ is the normal attenuation.

  Conceptually, this is the behavior of photons bouncing off several surfaces of a scene. While it's a very simple model, it's impossible to solve analytically for anything but the most simple of scenes, mostly due to, for example, the radiance at $P0$ relies on $P1$, and $P1$ relies on $P0$.

  Another thing to remember is that while it is shown to be integrated over a sphere, it is almost always, and will be for the rest of this document, integrated over hemisphere $\Omega$ using either $f_r$ or $f_s$.

  Unfortunately, this formula does not work very well in regards to bidirectional path tracing. The reason is because BDPT requires to work in terms of surfaces rather than solid angle, ei, $v_0 \rightarrow v_1$. So now the rendering equation must be transformed from solid angle to surfaces:
  \begin{align}
    f_s(v \rightarrow \dot{v} \rightarrow \ddot{v}) &= f_s(P, \omega_i,
                                                      \omega_o)\\
    L_e(v \rightarrow \dot{v}) &= L_e(P, \omega_o)\\
    L_e(v \rightarrow \dot{v}) &= L_e^0(v) L_e^1(v \rightarrow \dot{v})
  \end{align}
    That is, instead of looking at a point $P$ with an incoming and outgoing
    angle $(\omega_i,\:\omega_o)$, look at the path from $P_{-1}$ ($v$) to
    $P_{+1}$ ($\ddot{v}$). More accurately, it's the transport between
    three different surfaces of the scene. In terms of SDFs, the surface
    is every point on an SDF map where $|map| \leq \epsilon$. There's no longer
    any integration over a hemisphere with solid angle $\omega_i$, it's now over
    every single surface in the scene. This will be explained in detail later.
\\
    In the case of $L_e$,
    DTOADQ [at least, for now], only has support for area-light. Thus consider:

@@

  \section{Bibliography}
  [1]
  \begin{align*}
    \Sigma_{k=1}^{\infty} \int_{M^{k+1}} L_e(v_0 \rightarrow v_1) G(v_0
    \leftrightarrow v_1)
    \Pi_{i=1}^{k-1} F_s(v_{i-1} \rightarrow v_i \rightarrow v_{i+1}) G(v_i
    \leftrightarrow v_{i+1})\\
    W_e^j(v_{k-1} \rightarrow v_k) dA(v_0) \ldots dA(v_k)
  \end{align*}
  [9]
  Samuel D. Butler, Experimental and Theoretical Basis for a closed-Form Spectral BRDF model

  [Henyey]
   Diffuse Radation in the Galaxy, 1942. L, G. Henyey and J. L. Greenstein. 
\end{document}
\message{ !name(test.tex) !offset(-562) }

### 2017-11-27 testdocs/test.tex
whatever

\documentclass{article}
\usepackage{amsmath}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{color}
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage[margin=1.15in]{geometry}

@@

  Conceptually, this is the behavior of photons bouncing off several surfaces of a scene. While it's a very simple model, it's impossible to solve analytically for anything but the most simple of scenes, mostly due to, for example, the radiance at $P0$ relies on $P1$, and $P1$ relies on $P0$.

  Another thing to remember is that while it is shown to be integrated over a sphere, it is almost always, and will be for the rest of this document, integrated over hemisphere $\Omega$ using either $f_r$ or $f_s$.

  Unfortunately, this formula does not work very well in regards to bidirectional path tracing. The reason is because BDPT requires to work in terms of surfaces rather than solid angle, ei, $v_0 \rightarrow v_1$. So now the rendering equation must be transformed from solid angle to surfaces:
  \begin{align}
    f_s(v \rightarrow \dot{v} \rightarrow \ddot{v}) &= f_s(P, \omega_i,
                                                      \omega_o)\\
    L_e(v \rightarrow \dot{v}) &= L_e(P, \omega_o)\\
    L_e(v \rightarrow \dot{v}) &= L_e^0(v) L_e^1(v \rightarrow \dot{v})
  \end{align}
    That is, instead of looking at a point $P$ with an incoming and outgoing
    angle $(\omega_i,\:\omega_o)$, look at the path from $P_{-1}$ ($v$) to
    $P_{+1}$ ($\ddot{v}$). More accurately, it's the transport between
    three different surfaces of the scene. In terms of SDFs, the surface
    is every point on an SDF map where $|map| \leq \epsilon$. There's no longer
    any integration over a hemisphere with solid angle $\omega_i$, it's now over
    every single surface in the scene. This will be explained in detail later.
\\
    In the case of $L_e$,
    DTOADQ [at least, for now], only has support for area-light. Thus consider:

@@

    The cos term, used for the projected solid angle in irradiance, no longer
    applies when dealing with area. This and $d\omega_i$ now become a
    generalized geometry term, G, that converts a PDF with respect to solid area
    using Jacobian mapping, which involves the inverse squared distance, and the
    cosine angle between the geometric normals at $v$ and $\dot{v}$:

@@

    where $s$ is the light-path length, and $t$ is the eye-path length. In
    DTOADQ, they are limited to $s+t \leq 8$[TODO]. Finally, to transform
    $\bar{v}$ into two seperate paths, $\frac{f_j(\bar{v}_{s,
        t})}{p(\bar{v}_{s, t})}$ is split into two with a connection edge $c$
  \begin{align}
    \frac{f_j(\bar{v}_{s, t})}{p(\bar{v}_{s, t})} \equiv
    \frac{f^L(\bar{y})}{p(\bar{y})} c(\bar{y}_s \leftrightarrow \bar{z}_t)
    \frac{f^E(\bar{z})}{p(\bar{z})}  
  \end{align}

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{color}
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage[margin=1.15in]{geometry}
\author{aodq}

@@

  Conceptually, this is the behavior of photons bouncing off several surfaces of a scene. While it's a very simple model, it's impossible to solve analytically for anything but the most simple of scenes, mostly due to, for example, the radiance at $P0$ relies on $P1$, and $P1$ relies on $P0$. Another thing to remember is that while it is shown to be integrated over a sphere, it is usually shown to be integrated over hemisphere $\Omega$ using either $f_r$ or $f_s$.

  To compute this unbiasedly, it is required to use PDFs as described before to approximate the integral using Monte Carlo simulation. The technique is to generate $N$ uniformly random samples, weight them by their probability distribution, and then average the results:

  \begin{align}
   \int{f(x)} \: \approx \frac{1}{N}\Sigma_0^N{\frac{f(x)}{p(x)}}
  \end{align}

  With standard "backward" path tracing, a photon would be emitted from a light source and scatter in the scene until it hit an 'eye' or 'camera'. While this is what happens in reality, in computer graphics, most of the samples never end up hitting the camera/eye, so it is much more efficient to instead start from the eye, and end at an emitter/light source. In this case, since we are integrating over solid angle, the probably distribution function would be related to sampling the BRDF. So for example, on a specular surface, the PDF is $1.0$ where $\omega_o = reflect(\omega_i, N)$ and $0.0$ otherwise. An obvious optimization is to only sample over the valid BSDF angles, which is known as importance sampling. In DTQ, there are three BSDF functions:

  \begin{list}{}{}
  \item BSDF Spectrum: The albedo at $(P,\:\omega_i,\:\omega_o)$
  \item BSDF Sample: Samples a $\omega_o$ for a $(P,\:\omega_i)$
  \item BSDF PDF: The probability distribution of $(P,\:\omega_i,\:\omega_o)$
  \end{list}

  There are many more optimizations to be made as well. For example, at each scattering event, an additional photon can be sent towards each emitter. This is what is known as next-event estimation. While this improves performance drastically, naively averaging each contribution is a problem, because each path has a different probability to their paths/contributions. The technique to sample them properly, multiple importance sampling, is related to BDPT, however it will be detailed later. The important thing to understand is that, in this sampling strategy, there is a new PDF introduced which relates to the probability of a path being generated, and this is critical to understand the concept of BDPT.

  Now, the optimization that is of focus in DTQ is Bidirectional Path Tracing. Instead of starting from an eye or light, a 'photon' (path) is generated from both, allowed to scatter in the scene for a few paths (the length is determined by Russian Roulette described later), and connected. It's not exactly the end-points of the paths that are being connected, but each vertex generated is connected to each other. [SHOW EXAM{E}

  ]This actually has an interesting correlation to next-event estimation, as it could be seen as 'extending' the amount of emitters that can be connected to.

  Unfortunately, this formula does not work with BDPT, as it is necessary to transform the formula to work in terms of surface areas rather than solid angle, ei, $v_0 \rightarrow v_1$. The transformation looks like so:
  \begin{align}
    f_s(v \rightarrow \dot{v} \rightarrow \ddot{v}) &= f_s(P, \omega_i,
                                                      \omega_o)\\
    L_e(v \rightarrow \dot{v}) &= L_e(P, \omega_o)\\
    L_e(v \rightarrow \dot{v}) &= L_e^0(v) L_e^1(v \rightarrow \dot{v})
  \end{align}
    That is, instead of looking at a point $P$ with an incoming and outgoing
    angle $(\omega_i,\:\omega_o)$, look at the path from $P_{-1}$ ($v$) to
    $P_{+1}$ ($\ddot{v}$). More accurately, it's the transport between
    three different surfaces of the scene. There's a small change to be made in the case of $L_e$, as DTOADQ [at least, for now], only has support for area-light. Thus consider:

@@

    Instead of working with solid angles, we now work with a geometry term, G, that converts a PDF with respect to solid angle to surface area, which involves the inverse squared distance, and the cosine angle between the geometric normals at $v$ and $\dot{v}$:

@@

    where $s$ is the light-path length, and $t$ is the eye-path length. In
    DTOADQ, they are limited to $s+t \leq DEPTH$, a kernel-defined macro. Finally, to transform
    $\bar{v}$ into two seperate paths, so that an eye and light path may be generated, $\frac{f_j(\bar{v}_{s,
        t})}{p(\bar{v}_{s, t})}$ is split into two with a connection edge $c$
  \begin{align}
    \frac{f_j(\bar{v}_{s, t})}{p(\bar{v}_{s, t})} \equiv
    \frac{f^L(\bar{y})}{p(\bar{y})} c(\bar{y}_s \leftrightarrow \bar{z}_t)
    \frac{f^E(\bar{z})}{p(\bar{z})}  
  \end{align}
